---
# IMPORTANT: Change settings here, but DO NOT change the spacing.
# Remove comments and add values where applicable.
# The descriptions below should be self-explanatory

title: "Question One" 
#subtitle: "This will appear as Right Header"

documentclass: "elsarticle"

# --------- Thesis title (Optional - set to FALSE by default).
# You can move the details below around as you please.
Thesis_FP: FALSE
# Entry1: "An unbelievable study with a title spanning multiple lines."
# Entry2: "\\textbf{Nico Katzke}" # textbf for bold
# Entry3: "A thesis submitted toward the degree of Doctor of Philosophy"
# Uni_Logo: Tex/Logo.png # Place a logo in the indicated location (from your root, e.g. defaults to ~/Tex/Logo.png) and uncomment this line. Leave uncommented for no image
# Logo_width: 0.3 # If using a logo - use this to set width (size) of image
# Entry4: "Under the supervision of: \\vfill Prof. Joe Smith and Dr. Frank Smith"
# Entry5: "Stellenbosch University"
# Entry6: April 2020
# Entry7:
# Entry8:

# --------- Front Page
# Comment: ----- Follow this pattern for up to 5 authors
AddTitle: TRUE # Use FALSE when submitting to peer reviewed platform. This will remove author names.
Author1: "Jessica Van der Berg"  # First Author - note the thanks message displayed as an italic footnote of first page.
Ref1: "Financial Econometrics 2021" # First Author's Affiliation
Email1: "20190565\\@sun.ac.za" # First Author's Email address


# Comment out below to remove both. JEL Codes only given if keywords also given.
keywords: "Question1 \\sep Finance\\sep Financial Econometrics" # Use \\sep to separate
JELCodes: "L250 \\sep L100"

# ----- Manage headers and footers:
#BottomLFooter: $Title$
#BottomCFooter:
#TopLHeader: \leftmark # Adds section name at topleft. Remove comment to add it.
BottomRFooter: "\\footnotesize Page \\thepage" # Add a '#' before this line to remove footer.
addtoprule: TRUE
addfootrule: TRUE               # Use if footers added. Add '#' to remove line.

# --------- page margins:
margin: 2.3 # Sides
bottom: 2 # bottom
top: 2.5 # Top
HardSet_layout: TRUE # Hard-set the spacing of words in your document. This will stop LaTeX squashing text to fit on pages, e.g.
# This is done by hard-setting the spacing dimensions. Set to FALSE if you want LaTeX to optimize this for your paper.

# --------- Line numbers
linenumbers: FALSE # Used when submitting to journal

# ---------- References settings:
# You can download cls format here: https://www.zotero.org/ - simply search for your institution. You can also edit and save cls formats here: https://editor.citationstyles.org/about/
# Hit download, store it in Tex/ folder, and change reference below - easy.
bibliography: Tex/ref.bib       # Do not edit: Keep this naming convention and location.
csl: Tex/harvard-stellenbosch-university.csl # referencing format used.
# By default, the bibliography only displays the cited references. If you want to change this, you can comment out one of the following:
#nocite: '@*' # Add all items in bibliography, whether cited or not
# nocite: |  # add specific references that aren't cited
#  @grinold2000
#  @Someoneelse2010

# ---------- General:
RemovePreprintSubmittedTo: TRUE  # Removes the 'preprint submitted to...' at bottom of titlepage
Journal: "Journal of Finance"   # Journal that the paper will be submitting to, if RemovePreprintSubmittedTo is set to TRUE.
toc: FALSE                       # Add a table of contents
numbersections: TRUE             # Should sections (and thus figures and tables) be numbered?
fontsize: 11pt                  # Set fontsize
linestretch: 1.2                # Set distance between lines.
link-citations: TRUE            # This creates dynamic links to the papers in reference list.

### Adding additional latex packages:
# header-includes:
#    - \usepackage{colortbl} # Add additional packages here.

output:
  pdf_document:
    keep_tex: TRUE
    template: Tex/TexDefault.txt
    fig_width: 3.5 # Adjust default figure sizes. This can also be done in the chunks of the text.
    fig_height: 3.5
abstract: |
  This document contains the detailed answers for question one of the Financial Econometric exam 2021. 
---

<!-- First: Set your default preferences for chunk options: -->

<!-- If you want a chunk's code to be printed, set echo = TRUE. message = FALSE stops R printing ugly package loading details in your final paper too. I also suggest setting warning = FALSE and checking for warnings in R, else you might find ugly warnings in your paper. -->

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, fig.width = 6, fig.height = 5, fig.pos="H", fig.pos = 'H')
# Note: Include = FALSE implies the code is executed, but not printed in your pdf.
# warning and message = FALSE implies ugly messages and warnings are removed from your pdf.
# These should be picked up when you execute the command chunks (code sections below) in your rmd, not printed in your paper!

# Lets load in example data, and see how this can be stored and later called from your 'data' folder.
if(!require("tidyverse")) install.packages("tidyverse")
library(tidyverse)
Example_data <- Texevier::Ex_Dat


pacman::p_install_gh("Nicktz/fmxdat")
library(tidyverse)
library(dplyr)
library(tbl2xts)
library(PerformanceAnalytics)
SA_bonds <- read_rds("data/SA_Bonds.rds")
BE_Infl <- read_rds("data/BE_Infl.rds")
bonds_2y <- read_rds("data/bonds_2y.rds")
bonds_10y <- read_rds("data/bonds_10y.rds")
usdzar <- read_rds("data/usdzar.rds")
ZA_Infl <- read_rds("data/ZA_Infl.rds")
IV <- read_rds("data/IV.rds")

```


<!-- ############################## -->
<!-- # Start Writing here: -->
<!-- ############################## -->

# Question 1 Yeild Spread \label{Introduction}

Question 1 requires an analysis of South Africa's Yield Spreads and local mid to longer dated yields bonds. There have been claims that the bond yields are the highest they have been in decades. The plot below confirms this. As seen in the graph, the lowest spread between the local bond market was during the 2007/2008 financial crises, afterwhich it dramatically increases in 2010. The dramatic increase was short lived, with the yield spread increasing slowly between 2011 and 2019. In 2020, the yield spread between the 10 Year and 2 year, as well as the yield spread between the 10 year and 3 month local bonds increased dramatically. The yield spread between the 2 year and 3 month local bonds also experienced an increase, however, this increase reached levels similar to those experienced in 2000/2001. 

In increase in the yield spread can be explained by the uncertainty in the markets during the still on-going COVID-19 pandemic. Investors rushed to raise liquidity amid the uncertainty and panic, particularly those regarded as having a hint of risk. South African government bonds did not escape the effect of the pandemic, with significant sales of the asset class by foreigners, causing yields to spike and prices to move lower. 

```{r}
## SA_Bonds 
plot2 <- SA_bonds %>% mutate("10 Year and 3 Month"=SA_bonds$ZA_10Yr - SA_bonds$SA_3M, "2 Year and 3 Month" = SA_bonds$ZA_2Yr - SA_bonds$SA_3M, "10 Year and 2 Year"= SA_bonds$ZA_10Yr-SA_bonds$ZA_2Yr) %>% select(date, "10 Year and 3 Month", "2 Year and 3 Month", "10 Year and 2 Year") %>% gather(yield_spread, points, -date) %>% ggplot() + 
    geom_line(aes(x=date, y=points, color=yield_spread)) +
    theme_bw() +  
    labs(x = "Dates", y = "Spread", title = "Yeild Spread in Local Bond Market", subtitle = "Comparing Yeild Spread Between 3m, 2Y and 10Y bonds", caption = "Note:\nOwn Calculations") + guides(col=guide_legend("Yield Spread Between:"))

plot2
```


This effect felt are not isolated to the South African bond market, with all emerging market local currency debt selling off in unison, as will be shown in the graphs below. This graph follows a similar pattern ad the local bonds yeild spread. 

```{r}
plot3 <- left_join(SA_bonds %>% select(date, ZA_10Yr), bonds_10y %>% group_by(bonds_10y$Name) %>% filter(Name=="US_10Yr") %>% ungroup() %>% arrange(date) %>% filter(date >= lubridate::ymd(19991206)) , by= "date") %>% select(-c("bonds_10y$Name", "Name")) %>% mutate( spread = ZA_10Yr - Bond_10Yr) %>% ggplot() + geom_line(aes(x=date, y=spread), color="purple") +
 theme_bw() +  
    labs(x = "Dates", y = "Spread", title = "Yield Spread Between US and SA 10 Year Bonds", subtitle = "", caption = "Note:\nOwn Calculations")

plot3
```

## USD/ZAR level 

The spreads of the 10-year bond yields can be used to gauge currencies. The general rule is that when the yield spread widens in favor of a certain currency, that currency will appreciate against other currencies. 

Yield spreads are often seen as driven by monetary policy. Differences in the exchange rate will drastically affect the expected yield. The graph below shows that this is true for longer term bonds, however, there is more volatility is shorter term bonds implying that the exchange rate is not that good of a predictor and that monetary policy changes will drastically affect the yield. 

```{r}
plot1 <- usdzar %>% ggplot()+ geom_line(aes(x=date, y=Price), color="blue") +
   
theme_bw() +  labs(x = "", y = "Prices (ZAR)", title = "USD/ZAR Exchange Rate", subtitle = "Data given in SA currency ", caption = "Note:\nOwn Calculations")
plot1


``` 


## Different Yeild Spreads

Comparing the 10 year and 2 year bond is important, so that investor can determine whether a bond is fairly priced, cheap or expensive. It is a sign of the risk premium for investing in one investment over another. 

```{r}



left_join(SA_bonds %>% select(date, ZA_10Yr), bonds_10y %>% tbl_xts(.,cols_to_xts= "Bond_10Yr", spread_by ="Name") %>% xts_tbl() %>% filter(date >= lubridate::ymd(19991206)) %>% select(date, AUS_10Yr, Canada_10Yr, EURO_10Yr,UK_10Yr) %>% arrange(date), by= "date") %>% mutate( ZA_AUS = ZA_10Yr - AUS_10Yr, ZA_Canada = ZA_10Yr -Canada_10Yr, ZA_EURO = ZA_10Yr - EURO_10Yr, ZA_UK = ZA_10Yr - UK_10Yr) %>% select(date, ZA_AUS,ZA_Canada, ZA_EURO, ZA_UK) %>% gather(country, spread, -date) %>%
 ggplot() + geom_line(aes(x=date, y=spread, color=country)) +
 theme_bw() +  
    labs(x = "Dates", y = "Spread", title = "Yeild Spread Between Different Countries and SA 10 Year Bonds", subtitle = "Countries include United Kingdom, Europe, Cananda and Australie", caption = "Note:\nOwn Calculations")


```


```{r}


left_join(SA_bonds %>% select(date, ZA_2Yr), bonds_2y %>% tbl_xts(.,cols_to_xts= "Bond_2Yr", spread_by ="Name") %>% xts_tbl() %>% filter(date >= lubridate::ymd(19991206)) %>% select(date, AUS_2yr, Canada_2yr, EURO_2yr,UK_2yr, US_2yr) %>% arrange(date), by= "date") %>% mutate( ZA_AUS = ZA_2Yr - AUS_2yr, ZA_Canada = ZA_2Yr -Canada_2yr, ZA_EURO = ZA_2Yr - EURO_2yr, ZA_UK = ZA_2Yr - UK_2yr, ZA_US = ZA_2Yr - US_2yr) %>% select(date, ZA_AUS,ZA_Canada, ZA_EURO, ZA_UK, ZA_US) %>% gather(country, spread, -date) %>%
 ggplot() + geom_line(aes(x=date, y=spread, color=country)) +
 theme_bw() +  
    labs(x = "Dates", y = "Spread", title = "Yeild Spread Between Different Countries and SA 2 Year Bonds", subtitle = "Countries include United Kingdom, Europe, Cananda, Australia, United States", caption = "Note:\nOwn Calculations")



```
## Inflation 
In principle, the yield spread contains information on expectations of future inflation that can be extracted as an estimate of them. Studies of US and other markets have demonstrated that the yield curve does contain information on expected and actual future levels of gross domestic product (GDP) growth, and can be a lead indicator of business cycle downturns. 

Although many studies indicate the inflation-predicting power of the yield curve in developed countries’ markets, little is known of the relationship in emerging economies. The graph below mostly supports the notion that the yield spread contains valuable information about expected inflation, where price refers to the inflation rate. However, it is important to notice that inflation has much higher volatility then yield spread. The graph below shows that the higher the current rate of inflation, the higher the yields will rise across the yield curve, as investors will demand this higher yield to compensate for inflation risk



```{r}
data <- left_join(SA_bonds %>% select(date, ZA_10Yr), bonds_10y %>% group_by(bonds_10y$Name) %>% filter(Name=="US_10Yr") %>% ungroup() %>% arrange(date) %>% filter(date >= lubridate::ymd(19991206)) , by= "date") %>% select(-c("bonds_10y$Name", "Name")) %>% mutate( spread = ZA_10Yr - Bond_10Yr) %>% select(date, spread)

left_join(ZA_Infl %>%  filter(date >= lubridate::ymd(19991206)) %>% select(-Name) , data, by = "date") %>% na.omit() %>% gather(Data, Values, -date) %>% ggplot() + geom_line(aes(x=date, y=Values, color=Data)) +
 theme_bw() +  
    labs(x = "Dates", y = "", title = "Comparing Inflation and Yield Spread", subtitle = "Yeild Spread is between US and ZAR 10 year bond", caption = "Note:\nOwn Calculations")
```

